\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-09-20 notes/2loopNLSM.tex
Fixed broken refs

We can select out both of these manifestly cubic sectors by selecting only $\varepsilon^+\varepsilon^+$ in light-cone gauge (i.e. SDYM) and one-minus at tree-level OR what $J$-theory and $YZ$-theory select with their on-shell states. Indeed, the $D$-dimensional description of $J$-theory is just the following blocks in the expansion of Yang-Mills given in \ref{Pavao:2022kog}
\begin{equation}
A(...,\bar{A}_k,...)_{\text{tree}} = \sum_{j\neq k}\Delta^{(jk)}_{\text{tree}}
\end{equation}
and similarly so at one-loop
\begin{equation}
A(...)_{\text{1-loop}} \equiv \Delta^{(\varnothing)}_{\text{1-loop}}\, .
\end{equation}
To recover NLSM at one-loop, we need to extract the $D$-dependent part that corresponds to an internal $YY$-loop from extra-dimensional scalars
\begin{eBox}
\begin{equation}
A^{\text{NLSM}}_{\text{1-loop}} \equiv \partial_D \Delta^{(\varnothing)}_{\text{1-loop}}\big|_{\varepsilon\rightarrow k}\, .
\end{equation}
\end{eBox}
Why must we take the derivative with respect to $D$? After all, $J$-theory and $YZ$-theory both have well defined propagators for internal $\bar{J}J$ and $\bar{Z}Z$ propagators. However, as we noted in the previous section, all the $J$ and $Z$ states must be on-shell in order to produce NLSM amplitudes. Thus, the unitarity cuts of $J$ theory at one-loop will not produce NLSM amplitudes. However, the internal $YY$-loop is a valid forward limit, since as constructed YZ theory is valid for off-shell Y-particles, and thus they serve as a valid forward limit. We will construct these one-loop integrands below in the next section.

@@

This integrand numerator with internal scalar loop is precisely what one would obtain from the Feynman rules of YZ-theory, absent the $XZ$ internal vector loop. For more background, we refer the reader to appendix \ref{}. 

>>>>

We can select out both of these manifestly cubic sectors by selecting only $\varepsilon^+\varepsilon^+$ in light-cone gauge (i.e. SDYM) and one-minus at tree-level OR what $J$-theory and $YZ$-theory select with their on-shell states. Indeed, the $D$-dimensional description of $J$-theory is just the following blocks in the expansion of Yang-Mills given in \cite{Pavao:2022kog}
\begin{equation}
A(...,\bar{A}_k,...)_{\text{tree}} = \sum_{j\neq k}\Delta^{(jk)}_{\text{tree}}
\end{equation}
and similarly so at one-loop
\begin{equation}
A(...)_{\text{1-loop}} \equiv \Delta^{(\varnothing)}_{\text{1-loop}}\, .
\end{equation}
To recover NLSM at one-loop, we need to extract the $D$-dependent part that corresponds to an internal $YY$-loop from extra-dimensional scalars
\begin{eBox}
\begin{equation}
A^{\text{NLSM}}_{\text{1-loop}} \equiv \partial_D \Delta^{(\varnothing)}_{\text{1-loop}}\big|_{\varepsilon\rightarrow k}\, .
\end{equation}
\end{eBox}
Why must we take the derivative with respect to $D$? After all, $J$-theory and $YZ$-theory both have well defined propagators for internal $\bar{J}J$ and $\bar{Z}Z$ propagators. However, as we noted in the previous section, all the $J$ and $Z$ states must be on-shell in order to produce NLSM amplitudes. Thus, the unitarity cuts of $J$ theory at one-loop will not produce NLSM amplitudes. However, the internal $YY$-loop is a valid forward limit, since as constructed YZ theory is valid for off-shell Y-particles, and thus they serve as a valid forward limit. We will construct these one-loop integrands below in the next section.

@@

This integrand numerator with internal scalar loop is precisely what one would obtain from the Feynman rules of YZ-theory, absent the $XZ$ internal vector loop. For more background, we refer the reader to \cref{sec:CKLagrangians}. 
